Comparison of geochemical datasets for “*Confirmation of Mg/Ca ratios as palaeothermometers in Atlantic limpet shells*”

### 2024-09-12 Supplementary files 2 - isotope graphs.qmd
Added time warped graphs into supplementary and changed dtw function to provide standard deviation for warped series

@@

  P1 <-
    MgCa %>%
    filter(sampleID == sample) %>%
    filter(relstd < 0.1) %>%
    filter(mg_ca >= lower & mg_ca <= upper) %>%
    ggplot() +
    aes(dist, mg_ca) +
    geom_path() +
    theme_cowplot(17) +
    labs(x = "", y = "Mg/Ca intensity ratio", title = sample)

  P2 <-
    D18O %>%
    filter(sampleID == sample) %>%
    ggplot() +
    aes(dist, d18O) +
    geom_path() +
    theme_cowplot(18) +
    scale_y_reverse() +
    labs(x = "Distance to edge (mm)", y = expression(paste(delta^{18}, "O (\u2030)")))

  P1 / P2 + plot_annotation(tag_levels = "a")
}

>>>>

Corr_data <- read.csv(here("data","Corr_data.csv"))

#This below caused problems
#%>% 
  #   pivot_wider(values_from = "value",names_from = "proxy") %>%
  # left_join(D18O %>% select(sampleID) %>% unique(),by="sampleID") %>%
  # pivot_longer(cols=c(d18o,mg_ca),values_to = "value",names_to = "proxy") %>% 
  # arrange(x)

@@

  P1.1 <-
    MgCa %>%
    filter(sampleID == sample) %>%
    filter(relstd < 0.1) %>%
    filter(mg_ca >= lower & mg_ca <= upper) %>%
    ggplot() +
    aes(dist, mg_ca) +
    geom_path() +
    theme_cowplot(17) +
    labs(x = "", y = "Mg/Ca intensity ratio", title = sample)

  P1.2 <-
    D18O %>%
    filter(sampleID == sample) %>%
    ggplot() +
    aes(dist, d18O) +
    geom_path() +
    theme_cowplot(18) +
    scale_y_reverse() +
    labs(x = "Distance to edge (mm)", y = expression(paste(delta^{18}, "O (\u2030)")))

   P2.1 <-
    Corr_data %>%
    filter(sampleID == sample) %>%
    filter(proxy == "mg_ca") %>%
    ggplot() +
    aes(x, value) +
    # geom_errorbar(aes(ymin = value - sd, ymax = value + sd, width = 1)) +
    geom_ribbon(aes(ymin = value - sd, ymax = value + sd), alpha = 0.5) +
    geom_path() +
    theme_cowplot(17) +
    labs(x = "", y = "")

  P2.2 <-
    Corr_data %>%
    filter(sampleID == sample) %>%
    filter(proxy == "d18o") %>%
          group_by(x) %>% 
      mutate(sd=sd(value)) %>% 
      ungroup() %>% 
    ggplot() +
    aes(x, value) +
    # geom_errorbar(aes(ymin = value - sd, ymax = value + sd, width = 0.2)) +
    geom_ribbon(aes(ymin = value - sd, ymax = value + sd), alpha = 0.5) +
    geom_path() +
    theme_cowplot(18) +
    scale_y_reverse() +
    labs(x = "Warped time index", y = "")

    P1.1 / P1.2 |  P2.1 / P2.2 + plot_annotation(tag_levels = "a")

}
